---
title: "p8105_hw1_tg2753"
author: "Tianchuan Gao"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1
Create a data frame comprised of:  
- a random sample of size 10 from a standard Normal distribution  
- a logical vector indicating whether elements of the sample are greater than 0  
- a character vector of length 10  
- a factor vector of length 10, with 3 different factor “levels”  
```{r create data frame}
df = tibble(
  random_sample = rnorm(10),
  logical_vec = random_sample > 0,
  character_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = c("bad", "bad", "bad", "mid", "mid", "mid","mid", "good", "good", "good")
    )
```

take the mean of each variable in the dataframe
```{r take mean, echo=TRUE}
mean(pull(df, random_sample))
mean(pull(df, logical_vec))
mean(pull(df, character_vec))
mean(pull(df, factor_vec))
```

We can see from the above results that we can take mean for numerical and logical variables while not for character or factor variables

```{r,eval=FALSE}
as.numeric(pull(df, logical_vec))
as.numeric(pull(df, character_vec))
as.numeric(pull(df, factor_vec))
```
I can convert logical variables into numerical outcomes 0 or 1.  
But I cannot convert character or factor variables into numerical variables.  
This helps explain why I cannot take the mean for character or factor variables.  

## Problem 2

Load Dataset
```{r}
data("penguins", package = "palmerpenguins")
```
Write a short description of the penguins dataset including:  
-the data in this dataset, including names / values of important variables 
```{r}
summary(penguins)
```

-the size of the dataset (using nrow and ncol)  
the dataset has `r nrow(penguins)` rows, `r ncol(penguins)` columns.

-the mean flipper length  
the mean of the flipper length is `r mean(pull(penguins,flipper_length_mm), na.rm=TRUE)` months.

Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

Export your first scatterplot to your project directory using ggsave
```{r}
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

